---
title: "StimuliGeneration"
author: "Alex Kale"
date: "1/22/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(gganimate)
library(RColorBrewer)
library(gridExtra)
library(grid)
```

This file contains code to generate stimuli for our uncertainty visualization heuristics experiment.

##Data Conditions

We need stimuli for which our heuristics predict maximally different CLES estimates (see _Pilot.Rmd_). We sample extreme levels of ground truth CLES (i.e., odds) because these data should produce the most extreme differences between heuristics corresponding to different visualization conditions. Similarly, we test two dramatically different levels of uncertainty (i.e., std_diff) because we expect the relative mean difference heuristic to produce especially large errors when uncertainty is low and thus visually small mean differences are not representative of reliability.

```{r}
# set up possible data conditions dataframe
std_diff <- c(1, 5) # different levels of uncertainty about the margin of victory
logodds <- seq(log(0.025/(1-0.025)), log(0.975/(1-0.975)), length.out = 10) # linear sampling of log odds for ground truth Pr(A > B)
odds <- 1 - 1 / (exp(logodds) + 1)
# odds <- c(0.025, 0.1, 0.25, 0.75, 0.9, 0.975)
teamAB <- c("A", "B") # factor for team
# name conditions
cond <- vector(mode="character", length=10)
for (i in 1:length(std_diff)) {
  for (j in 1:length(odds)) {
    cond[(i - 1) * length(odds) + j] <- paste(c(std_diff[i],"sd",round(odds[j], 3),"odds"), collapse="_")
  }
}
# cond <- c("low sd, 0.025 odds", "low sd, 0.1 odds", "low sd, 0.25 odds", "low sd, 0.75 odds", "low sd, 0.9 odds", "low sd, 0.975 odds",
#           "high sd, 0.025 odds", "high sd, 0.1 odds", "high sd, 0.25 odds", "high sd, 0.75 odds", "high sd, 0.9 odds", "high sd, 0.975 odds")
conds_df <- data.frame(
    "condition" = rep(cond, 2),
    "sd_diff" = sort(rep(std_diff, length(odds))),
    "odds_of_victory" = rep(odds, length(std_diff)),
    "Team" = sort(rep(teamAB, length(std_diff) * length(odds)))
)

# add column for the mean difference
conds_df$mean_diff <- - (conds_df$sd_diff * qnorm(conds_df$odds_of_victory)) # mean(B - A)

# compute the mean of distributions A and B
center <- 50 # set the center point between the score of A and B
conds_df$mean[conds_df$Team == "A"] <- center - conds_df$mean_diff[conds_df$Team == "A"] / 2
conds_df$mean[conds_df$Team == "B"] <- center + conds_df$mean_diff[conds_df$Team == "B"] / 2

# compute the sd of distributions A and B, assuming independent and equal variances
conds_df$sd <- sqrt(conds_df$sd_diff ^ 2 / 2)

# for HOPs and quantile dotplots we need to add draws to our dataframe
n <- 1000 # number of samples
n_dots <- 20 # number of dots for quantile dotplots
conds_df$sample_n <- n
conds_df <- conds_df %>% as.tibble() %>%
  mutate(draws=pmap(list(sample_n, mean, sd), rnorm), # get a list of draws from the distribution for each condition
         draw_n=list(seq(1, n)), # number each sample in order to animate multiple views simultaneously
         quantiles=map(draws, ~ quantile(unlist(.x), ppoints(n_dots))) # use draw to get quantiles
         ) # leave these draws and quantiles nested in the dataframe for later use since they are not relevant to most visualizations

# save conds_df with the draws used to create these stimuli (for use in analysis)
save(conds_df, file = "stimuli/conds_df.Rda")

# print
head(conds_df)
```

##Visualization Stimuli

We create one of each plot type for each data condition above and save to a folder called stimuli.

```{r echo=FALSE}
# need a color scale for teams A and B
teams <- as.factor(c("A","B"))
tColors <- brewer.pal(length(teams), "Set1")
names(tColors) <- levels(teams)
colScale <- scale_colour_manual(values = tColors)
```

```{r echo=FALSE}
# function to draw captions in a consistent location relative to other text
wrap_label <- function(label, char_width) {
  return(lapply(strwrap(label, width = char_width, simplify = FALSE), paste, collapse="\n"))
}
```


```{r}
# select number of draws for HOPs conditions
n_draws_hops <- 50

# select limits for x-axis
data_domain <- c(38, 62)

# set plot dimensions
dims_pix <- c(770, 462) # pixel dimensions
ppi <- 75 # assume 75 ppi for the avg monitor
dims <- dims_pix / ppi # dimensions in inches

# geom sizes
means_size <- 3
HOPs_size <- 10
HOPs_mean_size_factor <- 1.5
interval_mean_size_factor <- 1.85
title_size <- 18
caption_size <- 16
char_before_wrap <- 86

# cycle through rows in the table of data conditions
for (c in unique(conds_df$condition)) {
  # isolaten data for the current condtion
  use_df <- conds_df %>% filter(condition %in% c) #%>% arrange(desc(Team))
  
  # means only
  plt <- use_df %>% ggplot(aes(x=mean, y=reorder(Team, desc(Team)), color=Team)) +
    geom_point(size=means_size) +
    theme_bw() +
    colScale +
    xlim(data_domain[1], data_domain[2]) +
    labs(
      title="Scores in Previous Rounds of TeamCrossword",
      x="Average of Past Scores",
      y=NULL,
      caption=wrap_label("Dots represent the average score in past games for each team.", char_before_wrap)
    ) +
    theme(
      plot.title=element_text(size=title_size),
      plot.caption=element_text(size=caption_size, hjust=0)
    )
  fname <- paste("stimuli/means_only-", c,".svg", sep = "")
  ggsave(file=fname, plot=plt, width=dims[1], height=dims[2])
  
  # intervals only
  plt <- use_df %>% ggplot(aes(y=mean, x=reorder(Team, desc(Team)), color=Team)) +
    geom_errorbar(aes(ymin=mean+qnorm(0.025)*sd, ymax=mean+qnorm(0.975)*sd, width=0)) +
    coord_flip() +
    theme_bw() +
    colScale +
    ylim(data_domain[1], data_domain[2]) +
    labs(
      title="Scores in Previous Rounds of TeamCrossword",
      x=NULL,
      y="Range Containing 95% of Past Scores",
      caption=wrap_label("Intervals represent the span of past scores for 95% of games played by each team.", char_before_wrap)
    ) +
    theme(
      plot.title=element_text(size=title_size),
      plot.caption=element_text(size=caption_size, hjust=0)
    )
  fname <- paste("stimuli/intervals_only-", c,".svg", sep = "")
  ggsave(file=fname, plot=plt, width=dims[1], height=dims[2])

  # hops
  plt <- use_df %>% select(-one_of(c("quantiles"))) %>% unnest() %>%
    filter(draw_n %in% 1:n_draws_hops) %>% # filter to set number of draws
    ggplot(aes(y=draws, x=reorder(Team, desc(Team)), color=Team)) +
    geom_point(shape=124, size=HOPs_size) +
    coord_flip() +
    theme_bw() +
    colScale +
    ylim(data_domain[1], data_domain[2]) +
    labs(
      title="Scores in Previous Rounds of TeamCrossword",
      y="Past Scores",
      x=NULL,
      caption=wrap_label("Lines represent past scores in individual games for each team.", char_before_wrap)
    ) +
    theme(
      plot.title=element_text(size=title_size),
      plot.caption=element_text(size=caption_size, hjust=0)
    ) +
    transition_manual(draw_n)
  hops <- animate(plt, fps=2.5, res=100, width=dims[1]*100, height=dims[2]*100)
  fname <- paste("stimuli/HOPs-", c,".gif", sep = "")
  anim_save(filename = fname, animation = hops)

  # quantile dotplots
  # plt <- use_df %>% select(-one_of(c("draws", "draw_n"))) %>% unnest() %>%
  #   ggplot(aes(x=quantiles, fill=Team)) +
  #   geom_dotplot(binwidth=.75, binaxis = "x", binpositions="all") +
  #   theme_bw() +
  #   scale_fill_brewer(palette="Set1") +
  #   xlim(data_domain[1], data_domain[2]) +
  #   labs(
  #     title="Scores in Previous Rounds of TeamCrossword",
  #     x="Past Scores",
  #     y="Proportion of Past Scores",
  #     caption=wrap_label("Each dot represents 5% of past scores for each team.", char_before_wrap)
  #   ) +
  #   facet_grid(Team ~ .) +
  #   theme(
  #     strip.background = element_blank(),
  #     strip.text.x = element_blank(),
  #     plot.title=element_text(size=title_size),
  #     plot.caption=element_text(size=caption_size, hjust=0)
  #   )
  # fname <- paste("stimuli/QDPs-", c,".svg", sep = "")
  # ggsave(file=fname, plot=plt, width=dims[1], height=dims[2])

  # densities
  # plt <- use_df %>% select(-one_of(c("draws", "draw_n"))) %>% unnest() %>%
  #   ggplot(aes(x=quantiles, color=Team)) +
  #   geom_density() +
  #   theme_bw() +
  #   colScale +
  #   xlim(data_domain[1], data_domain[2]) +
  #   labs(
  #     title="Scores in Previous Rounds of TeamCrossword",
  #     x="Past Scores",
  #     y="Proportion of Past Scores",
  #     caption=wrap_label("The height of the line represents the proportion of past scores for each team.", char_before_wrap)
  #   ) +
  #   theme(
  #     plot.title=element_text(size=title_size),
  #     plot.caption=element_text(size=caption_size, hjust=0)
  #   )
  # fname <- paste("stimuli/densities-", c,".svg", sep = "")
  # ggsave(file=fname, plot=plt, width=dims[1], height=dims[2])

  # intervals with means
  plt <- use_df %>% ggplot(aes(y=mean, x=reorder(Team, desc(Team)), color=Team)) +
    geom_pointrange(aes(ymin=mean+qnorm(0.025)*sd, ymax=mean+qnorm(0.975)*sd), show.legend=FALSE, fatten=means_size*interval_mean_size_factor) +
    geom_line(aes(y=mean-1000)) + geom_point(aes(y=mean-1000)) + # hack to get legend symbols oriented properly
    coord_flip() +
    theme_bw() +
    colScale +
    ylim(data_domain[1], data_domain[2]) +
    labs(
      title="Scores in Previous Rounds of TeamCrossword",
      y="Past Scores",
      x=NULL,
      caption=wrap_label("Dots represent the average score in past games for each team, and intervals represent the span of past scores for 95% of games.", char_before_wrap)
    ) +
    theme(
      plot.title=element_text(size=title_size),
      plot.caption=element_text(size=caption_size, hjust=0)
    )
  fname <- paste("stimuli/intervals_w_means-", c,".svg", sep = "")
  ggsave(file=fname, plot=plt, width=dims[1], height=dims[2])

  # hops with means
  plt <- use_df %>% select(-one_of(c("quantiles"))) %>% unnest() %>%
    filter(draw_n %in% 1:n_draws_hops) %>% # filter to set number of draws
    ggplot(aes(y=mean, x=reorder(Team, desc(Team)), color=Team)) +
    geom_point(size=means_size*HOPs_mean_size_factor) +
    geom_point(aes(y=draws), shape=124, size=HOPs_size) +
    coord_flip() +
    theme_bw() +
    colScale +
    ylim(data_domain[1], data_domain[2]) +
    labs(
      title="Scores in Previous Rounds of TeamCrossword",
      y="Past Scores",
      x=NULL,
      caption=wrap_label("Dots represent the average score in past games for each team, and lines represent past scores in individual games.", char_before_wrap)
    ) +
    theme(
      plot.title=element_text(size=title_size),
      plot.caption=element_text(size=caption_size, hjust=0)
    ) +
    transition_manual(draw_n)
  hops <- animate(plt, fps=2.5, res=100, width=dims[1]*100, height=dims[2]*100)
  fname <- paste("stimuli/HOPs_w_means-", c,".gif", sep = "")
  anim_save(filename = fname, animation = hops)
}
```
